\chapter{Referéncias}

NASA, (DSCOVR: EPIC,) 16 10 2023. [En línea]. Available: https://epic.gsfc.nasa.gov/.

NASA, (eclipse,) 16 10 2023. [En línea]. Available: https://eclipse.gsfc.nasa.gov/SEdecade/SEdecade1991.html.
D. B. C. T. Amir Caspi, (arxiv,) 1 Junio 2020. [En línea]. Available: https://arxiv.org/abs/2004.09658. [Último acceso: 16 Octubre 2023].

Exploratorium, (Exploratorium,) 15 10 2023. [En línea]. Available: https://www.exploratorium.edu/es/eclipse/por-qu%C3%A9-estudiamos-los-eclipses-solares.

T. Humphrey, «bbc,» 14 7 2019. [En línea]. Available: https://www.bbc.com/news/uk-england-hampshire-66188381.

V. G. A. M. Lugo Gozález, «Mechatronic design implemented in the development of virtual and physical prototypes,» Diciembre 2020. [En línea]. Available: https://www.researchgate.net/publication/348209704_Diseno_mecatronico_implementado_en_el_desarrollo_de_prototipos_virtuales_y_fisicos_Mechatronic_design_implemented_in_the_development_of_virtual_and_physical_prototypes. [Último acceso: 03 Noviembre 2023].

C. J. L. O. A. L. d. M. C. Jiménez Fernández, «Redalyc,» Diciembre 2010. [En línea]. Available: http://www.redalyc.org/articulo.oa?id=36815118002. [Último acceso: 03 Noviembre 2023].

S. Laoyan, «asana,» 29 septiembre 2022. [En línea]. Available: https://asana.com/es/resources/waterfall-project-management-methodology. [Último acceso: 03 Noviembre 2023].

M. Kramer, «space,» 02 Febrero 2015. [En línea]. Available: https://www.space.com/28481-spacex-launches-dscovr-satellite.html. [Último acceso: 15 Octubre 2023].
zkl, «zkl doc,» [En línea]. Available: https://blog.zerokol.com/2012/09/arduinofuzzy-uma-biblioteca-fuzzy-para.html. [Último acceso: 1 Diciembre 2023].
E. C. Alvarez, «Mexico desconocido,» 15 10 2023. [En línea]. Available: https://www.mexicodesconocido.com.mx/eclipses-yucatan-cultura-maya-aztecas.html.
NESDIS, «National Environmental Satellite, Data and Information Service.,» 16 10 2023. [En línea]. Available: https://www.nesdis.noaa.gov/current-satellite-missions/currently-flying/dscovr-deep-space-climate-observatory.
NASA, «cubesat,» 16 10 2023. [En línea]. Available: https://www.cubesat.org/past-launches/2017-delta-ii-jpss-1-elana14.
F. Meconi, «Terraza al cosmos,» 2020. [En línea]. Available: https://www.terrazaalcosmos.com.ar/eclipsor.
El mundo Madrid, «El mundo,» 22 Junio 2016. [En línea]. Available: https://www.elmundo.es/ciencia/2016/06/22/576abf57268e3ebc3f8b45ed.html. [Último acceso: 20 10 2023].
NASA, «EPIC,» 14 Octubre 2023. [En línea]. Available: https://epic.gsfc.nasa.gov/enhanced?date=2023-10-14. [Último acceso: 16 Octubre 2023].
